Debugging by \textit{lastChange}

### 2010-10-22 trunk/papers/pldi2011/sigplanconf-template.tex
narrow paragraphs only change

In this important case of reproducible bugs, \textit{lastChange} are more effective than breakpoints. In the case of logically deterministic program execution, we can use the result from a \textit{lastChange} operation to set a conditional breakpoint then re-execute the program to position the execution trace backwards from our first breakpoint. %(This may be a useful adjunct for Querypoint debuggers to implement, but this backwards motion in the execution logic is not required for Querypoint debugging.) Thus in this case Querypoint debugging can do the same kinds of things as conventional breakpoints just more automatically.

@@

>>>>

In this important case of reproducible bugs, \textit{lastChange} are
more effective than breakpoints. In the case of logically
deterministic program execution, we can use the result from a
\textit{lastChange} operation to set a conditional breakpoint then
re-execute the program to position the execution trace backwards from
our first breakpoint.

%(This may be a useful adjunct for Querypoint debuggers to implement, but this backwards motion in the execution logic is not required for Querypoint debugging.) Thus in this case Querypoint debugging can do the same kinds of things as conventional breakpoints just more automatically.

@@

\subsection{Reproduction point}
